Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-11-05 Thesis/chapter/061-results-emma.tex
write about mars

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{rational behind including $v_{cal}$ and $\lambda$ as optimizands}
The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ 
were included as dependent variables with the objective to maximize with a relative weight of 0.05 each.
The idea was to maximize $v_{cal}$ and minimize $\lambda$ in order to minimize the process time. 
Another thought behind including $v_{cal}$ and $\lambda$ was to test if the algorithm would correctly predict those. 
%
%Three major flaws behind this consideration became obvious with time: 
%
\
\ds{
(1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ (\oc{}/\h{} instead of \oc{}/\minutes{}) and $\lambda$, respectively. 
The algorithm will tend to include those values into the prediction function for 
all dependent variables and possibly exclude others which have more influence 
on $\gamma$ and $\rho$ (see equations \ref{eq:emma-G4}? and \ref{eq:emma-phd4}?).
%
(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
%
(3) needlessly making the problem more complicate %, important time (around 10\% of the samples) could have been replaced with more insightful samples. 
\begin{itemize}
    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
heating rate was one of the dependent variables with the intention of minimizing the variable. 
It can also be used as test to see how well the EMMA performs (or rather, more precisely MARS).
Even if it didn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
Overall there were too many variables involved for such a small dataset
        that means that adding dependent variables influences \td{previous variables}
\end{itemize}
}
\td{look at emma papers}
\td{change G to gamma and write enr to every figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{rational behind including $v_{cal}$ and $\lambda$ as optimizands}
The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ 
were included as dependent variables with the objective to maximize with a relative weight of 0.05 each.
The idea was to maximize $v_{cal}$ and minimize $\lambda$ in order to minimize the process time. 
Another thought behind including $v_{cal}$ and $\lambda$ was to test if the algorithm would correctly predict those. 
%
%Three major flaws behind this consideration became obvious with time: 
%
\
\ds{
(1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ (\oc{}/\h{} instead of \oc{}/\minutes{}) and $\lambda$, respectively. 
The algorithm will tend to include those values into the prediction function for 
all dependent variables and possibly exclude others which have more influence 
on $\gamma$ and $\rho$ (see equations \ref{eq:emma-G4}? and \ref{eq:emma-phd4}?).
%
(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
%
(3) needlessly making the problem more complicate %, important time (around 10\% of the samples) could have been replaced with more insightful samples. 
\begin{itemize}
    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
heating rate was one of the dependent variables with the intention of minimizing the variable. 
It can also be used as test to see how well the EMMA performs (or rather, more precisely MARS).
Even if it didn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
Overall there were too many variables involved for such a small dataset
        that means that adding dependent variables influences \td{previous variables}
\end{itemize}
}
\td{look at emma papers}
\td{change G to gamma and write enr to every figure}
\td{in \cite{friedman1991multivariate} the model is said to work well on $\frac{N}{n}$ ratios (aka events per predictor varibale (EPV)) of 20-50. 
EPV is around 5 for this model.
Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
}
